Demes: a standard format for demographic models

### 2022-05-25 software-table.tex
Update software table

\dadi &
       Simulate SFS from Demes models, infer demographic history and distributions of fitness effects~\citep{gutenkunst2009inferring}.
    \\

\fwdpy &
    Forward-time Wright-Fisher simulation \citep{thornton2014cpp,thornton2019-nu}.\\

\gadma &
    Demographic inference \citep{noskova2020gadma}.\\

\moments &
    Compute expected diversity statistics (SFS, LD) and perform
    demographic inference using summary statistics
    \citep{jouganous2017inferring,ragsdale2019models}.\\

\msprime &
    Coalescent simulation of Demes models, including command line
    interface~\citep{kelleher2016efficient,kelleher2020coalescent,baumdicker2021-iu}.\\

>>>>

\dadi &
   Optimizes parameters in models of demographic history and distributions of fitness effects using SFS~\citep{gutenkunst2009inferring}. Can simulate SFS from Demes models.
    \\

\demesslim &
    Loads Demes models into the \slim\ forward simulator \citep{haller2019slim}.\\

\fwdpy &
   Simulates the Wright-Fisher model forward in time \citep{thornton2014cpp,thornton2019-nu}. Demes is the preferred format for specifying a demographic model.\\

\gadma &
    Infers models of demographic history \citep{noskova2020gadma}. Outputs Demes models and visualizations. \\

\moments &
    Optimizes parameters in models of demographic history using SFS and linkage disequilibrium statistics
    \citep{jouganous2017inferring,ragsdale2019models}. Models to be optimized can be specified in Demes.\\

\msprime &
    Simulates population genetic models using tree sequences~\citep{kelleher2016efficient,kelleher2020coalescent,baumdicker2021-iu}. Demographic history models can be specified using Demes.\\
